Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-04 reviews.Rmd
fix references

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
manuscript-src : "headings"

cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
---

@@

Terminology and Conceptual Clarity:
* Reviewer Concern: The terminology used, particularly “theoretical risk,” was seen as potentially confusing and misaligned with existing literature, such as the concept of severity.
* Our Response: We provided additional references and explanations to support our terminology. We believe our terms accurately reflect the concepts within our Bayesian framework, but we differentiated our terminology further from frequentist reasoning.

@@

However, the mere use of the likelihood ratio in the Bayes theorem can not be grounds to reduce Bayesianism to likelihood ratios.

>>>>

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
manuscript-src : "headings"
bibliography   : references.bib
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
---

@@

Terminology and Conceptual Clarity:

* Reviewer Concern: The terminology used, particularly “theoretical risk,” was seen as potentially confusing and misaligned with existing literature, such as the concept of severity.
* Our Response: We provided additional references and explanations to support our terminology. We believe our terms accurately reflect the concepts within our Bayesian framework, but we differentiated our terminology further from frequentist reasoning.

@@

The mere use of the likelihood ratio in the Bayes theorem can not be grounds to reduce Bayesianism to likelihood ratios.
